\begin{thebibliography}{99}
    \bibitem{ref:1} R.P.Chhabra, "Bubbles, Drops, and Particles in Non-Newtonian Fluids," CRC, Taylor \& Francis, 2007.
    \bibitem{ref:2} M.Ohta, E.Iwasaki and Y.Yoshida, "A numerical study of the motion of a spherical," J. Nonnewton. Fluid Mech., vol.116, pp.95-111, 2003.
    \bibitem{ref:3} M.Ohta, E.Iwasaki, E.Obata and Y.Yoshida, "Dynamic Processes in a Deformed Drop Rising through Shear-Thinning Fluid," J. Non-Newtonian Fluid Mech., vol.132, no.1-3, pp. 100-107, 2005.
    \bibitem{ref:4} L.Zhang, C.Yang and Z.Mao, "Numerical simulation of a bubble rising in shear-thinning fluids," Journal of Non-Newtonian Fluid Mechanics, vol.165, pp.555-567, 2010.
    \bibitem{ref:5} Y.Yamada, T.Takashima, H.Mori, “Shear-thinning性流体脱泡における微小気泡周りの局所流れに関する検討,” 化学工学会　研究発表講演要旨集, p.294, 2007.
    \bibitem{ref:6} S.van denWildenberg, X.Jia, J.Léopoldès and A.Tourin, "Ultrasonic tracking of a sinking," Scientific Reports, 2019.
    \bibitem{ref:7} A.V.Egorichev, P.N.Kravchun and K.V.Chernyshev, "Acoustic boundary layer," Soviet Physics Journal, vol.22, p.1200-1204, 1979.
    \bibitem{ref:8} M.Iwamuro, T.Watamura , K.Sugiyama, “超音波照射された擬塑性流体中における物体の高速化,” 大阪大学修士論文, 2020.
    \bibitem{ref:8-5} Putz, A. M. V., Burghelea, T. I., Frigaard, I. A. and Martinez, D. M., Settling of an Isolated Spherical Particle in a Yield Stress Shear Thinning Fluid, Physics of Fluids, Vol. 20(3), 033102 (2008).
    \bibitem{ref:suzuki2021} Y.Suzuki, "粘弾性流体のレオロジーの基礎", 色材協会誌, vol 84, no.2, p.47-51, 2011.
    \bibitem{ref:9} M.Iwamuro, T.Watamura and K.Sugiyama, "The Influence of Ultrasound Irradiation on Falling Sphere in Pseudo-Plastic Fluid.," 混相流, vol.33, no.1, p.87-95, 2019.
    \bibitem{ref:10} T.Shiratori, Y.Tanaka and Y.Murai, "Rapid Rheological Characterization of a Viscoelastic Fluid Based on Spatiotemporal Flow Velocimetry," Exp. Thermal Fluid Sci., vol.71, pp.1-13, 2016.
    \bibitem{ref:12} M.T.Arigo, G.H.Mckinley, "The Effects of Viscoelasticity on the Transient Motion of a Sphere in a Shear-Thinning Fluid," Journal of Rheology, vol.41(103), 1996.
    \bibitem{ref:sakanishi} A.Sakanishi, "〈緩和時間〉", 日本バイオロジー学会誌, vol.3, no.2, p.50, 1989.
    \bibitem{ref:t-koshiba1996} V.D.Alves, F.Freitas, N.Costa, M.Carvalheira, R.Oliveira, M.P.Gonçalves, M.A.M.Reis, "Effect of temperature on the dynamic and steady-shear rheology of a new microbial extracellular polysaccharide produced from glycerol byproduct", Carbohydrate Polymers, vol.79, p.981-988, 2010.
    \bibitem{ref:Rahimi2007} S.Rahimi, A.Peretz, "On Shear Rheology of Gel Propellants", Propellants, Explosives, Pyrotechnics, vol.32, no.2, 2007.
    \bibitem{ref:Agi2018} A.Agi, R.Junin, J.Gbonhinbor, M.Onyekonwu, "Natural polymer fow behaviour in porous media for enhanced oil recovery applications: a review", Journal of Petroleum Exploration and Production Technology, vol.8, p.1349-1362, 2018.
\end{thebibliography}